Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
Adds references to Intro
Fixes #47

A storage system implements abstractions designed to persistently store
data and must exhibit a high level of correctness to prevent data loss.
Storage systems have evolved around storage devices that often were
orders of magnitude slower than CPU and memory and therefore can
dominate overall performance if not used carefully. Over the last few
decades members of the storage systems community have developed
ingenious strategies to meet correctness requirements while somewhat
hiding the latency of traditional storage media. To avoid lock-in by a
particular vendor, users of storage systems have preferred systems with
highly standardized APIs and lowest common denominator abstract data
types such as blocks of bytes and byte stream files.

A number of recent developments are disrupting traditional storage
systems: (1) the falling prices of flash storage and the availability of
new types of non-volatile memory that are orders of magnitude faster
than traditional spinning media are moving overall performance
bottlenecks away from storage devices to CPUs and networking, and
pressure storage systems to shorten their code paths and incorporate new
optimizations; (2) demand for managing structured data and flexible
consistency semantics at scale pressure big data processing systems to
use storage abstractions that can meet these demands; and (3)
production-quality scalable storage systems available as open source
software have established and are continuing to establish new, \emph{de
facto} API standards at a faster pace than traditional standards bodies.

@@

To illustrate the benefits and challenges of this approach we examine
the programmability of Ceph~\cite{weil_ceph_2006}, the increasingly
popular, production-level open-source distributed storage system.
Something of a storage swiss army knife, Ceph supports file, block, and
object interfaces simultaneously in a single cluster. Ceph's Reliable Autonomous Distributed Object Storage (RADOS) system is a cluster of storage
devices (OSDs) that provide Ceph with data durability and integrity
using replication, erasure-coding, and scrubbing~\cite{weil_rados_2007}. 
% By introducing
% programmability concepts into Ceph, we can build new services by
% carefully exposing internal storage services to applications.

>>>>

A storage system implements abstractions designed to persistently store
data and must exhibit a high level of correctness to prevent data loss.
Storage systems have evolved around storage devices that often were
orders of magnitude slower than CPU and memory, and therefore could
dominate overall performance if not used carefully. Over the last few
decades members of the storage systems community have developed
ingenious strategies to meet correctness requirements while somewhat
hiding the latency of traditional storage media~\cite{brewer_disks_2016}. To avoid lock-in by a
particular vendor, users of storage systems have preferred systems with
highly standardized APIs and lowest common denominator abstract data
types such as blocks of bytes and byte stream files~\cite{armbrust_view_2010}.

A number of recent developments are disrupting traditional storage
systems: (1) the falling prices of flash storage and the availability of
new types of non-volatile memory that are orders of magnitude faster
than traditional spinning media are moving overall performance
bottlenecks away from storage devices to CPUs and networking, and
pressure storage systems to shorten their code paths and incorporate new
optimizations~\cite{gray_tape_2007,gray_flash_2008}; (2) demand for managing structured data and flexible
consistency semantics at scale pressure big data processing systems to
use storage abstractions that can meet these demands~\cite{apache_contributors_parquet_2014}; and (3)
production-quality scalable storage systems available as open source
software have established and are continuing to establish new, \emph{de
facto} API standards at a faster pace than traditional standards bodies~\cite{snia_implementing_2014,linux_foundation_kinetic_2015}.

@@

To illustrate the benefits and challenges of this approach we examine
the programmability of Ceph~\cite{weil_ceph_2006}, the increasingly
popular, production-level open-source distributed storage system.
Something of a storage swiss army knife, Ceph supports file, block, and
object interfaces simultaneously in a single cluster~\cite{ceph_contributors_ceph_2010}. Ceph's Reliable Autonomous 
Distributed Object Storage (RADOS) system is a cluster of storage
devices (OSDs) that provide Ceph with data durability and integrity
using replication, erasure-coding, and scrubbing~\cite{weil_rados_2007}. 
% By introducing
% programmability concepts into Ceph, we can build new services by
% carefully exposing internal storage services to applications.
